A Prediction of the 2024 U.S. Election Outcome 

### 2024-11-04 paper/paper.qmd
need data part

---
title: "A Prediction of the 2024 U.S. Election Outcome "
subtitle: "A Bayesian Spline Regression Analysis of Kamala Harris's Winning"
author: 
  - Shanjie Jiao
  - Aman Rana
  - Kevin Shen
thanks: "Code and data are available at: [https://github.com/Jie-jiao05/2024_US_Election.git)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

## Overview paragraph

@@

## Estimand paragraph

@@

## Results paragraph
Using Bayesian spline regression analysis on the dataset provided by FiveThirtyEight [@FiveThirtyEight], this study forecasts the outcome of the 2024 U.S. election, predicting a victory for Kamala Harris.

## Why it matters paragraph：

@@

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data we will discuss the MLR used in the prediction and the result of the MLR with its predictor variables and the response after transformation. @sec-dis the shortcomings of the study and areas for improvement will be described. @sec-Appendix-A A Deep Dive to a pollster will be conducted, and @sec-Appendix-B We will given a idealized survey and methodology

@@

We use the statistical programming language R [@citeR] to analysis the data which are extracted from the 2024 U.S. General President Election collected and published by FiveThirtyEight  [@citation later]. This paper will conduct a Multiple Linear Regression to do further prediction. In this model, we take numeric_grade, pollscore, sample_size as predictors, and pct as response.

>>>>

---
title: "A Prediction of the 2024 U.S. Election Outcome "
subtitle: "A Bayesian Spline Regression Analysis of Kamala Harris's Winning"
author: 
  - Shanjie Jiao
  - Aman Rana
  - Kevin Shen
thanks: "Code and data are available at: [https://github.com/Jie-jiao05/2024_US_Election.git)."
date: today
date-format: long
abstract: "The 2024 U.S. Presidential Election, set against a backdrop of economic and political challenges, features Donald Trump and Kamala Harris as the main candidates. This study uses Bayesian spline regression on polling data from FiveThirtyEight to predict the election outcome, capturing dynamic voter trends over time. Our analysis suggests a likely win for Kamala Harris. Given the U.S.’s global influence, this result could significantly impact international security, trade, geopolitics, and provide a clear insight of forthcoming policy directions."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

@@

@@

Using Bayesian spline regression analysis on the dataset provided by FiveThirtyEight [@FiveThirtyEight], this study forecasts the outcome of the 2024 U.S. election, predicting a victory for Kamala Harris.

@@

The remainder of this paper is structured as follows. @sec-data we will discuss the MLR used in the prediction and the result of the MLR with its predictor variables and the response after transformation. @sec-dis the shortcomings of the study and areas for improvement will be described. @sec-Appendix-A A Deep Dive to a pollster will be conducted, and @sec-Appendix-B We will given a idealized survey and methodology

@@

We use the statistical programming language R [@citeR] to analysis the data which are extracted from the 2024 U.S. General President Election collected and published by FiveThirtyEight  [@FiveThirtyEight]. This paper will conduct a Multiple Linear Regression to do further prediction. In this model, we take numeric_grade, pollscore, sample_size as predictors, and pct as response.
